Plot the within and between group distance in a bar plot

### 2020-01-17 scripts/33_distance_bar.Rmd
update

>>>>

```{r}
all <- bind_rows(data_frame(group = 'NY',distance = dists@dist),
    data_frame(group = 'N',distance = N_dist),
    data_frame(group = 'Y',distance = Y_dist))

all %>% 
  ggboxplot(x = 'group', y = 'distance', add = 'jitter') +
  stat_compare_means(
    comparisons = list(c('NY', 'N'), c('NY','Y'), c('Y','N')),
    label = "p.signif",
    method = 'wilcox.test')
```
